\protect Connecting every bit of knowledge: \\ The structure of Wikipedia's First Link Network

### 2016-09-08 writeup/2016-04wikipedia-network/wikipedia-network.body.tex
revisions addressed

As a measure of influence, traversal funnels differs from traditional centrality measures such as degree centrality, betweenness centrality, and eigenvector centrality. 
Degree centrality characterizes how many articles have a first link to a particular topic, restricting influence to a single link. 
Betweenness centrality and eigenvalue centrality capture flow within the network more than a single link away. Unlike traversal funnels however, betweenness centrality and eigenvalue centrality reward nodes that simply happen to be in a cycle. In our sample network (see Fig.~\ref{fig:Centrality Measures}), node A is relatively central using both betweenness and eigenvector centrality although node A is simply the recipient of paths directed by node C. Eigenvector centrality even assigns the same centrality to nodes A, B, and C. In contrast, traversal funnels defines a path without a predetermined end node, following the progression of links to its culmination at the start of a cycle. Furthermore, traversal funnels provides an interpretable metric: a node's traversal funnels is the number of paths the node directs to the start of a cycle. 
Consequently, traversal funnels allow us to isolate the paths directed by node C without any spill over effect on other nodes in its cycle.

@@

By considering the FLN not only as collection of directly linked pairs of articles, but
as a flow, with accumulated references, cycles, and path-connected groups, we explore how the many articles in Wikipedia are organized and related.

>>>>

As a measure of influence, traversal funnels differs from traditional centrality measures such as degree centrality, betweenness centrality, and eigenvector centrality. 
Degree centrality characterizes how many articles have a first link to a particular topic, restricting influence to a single link. 
Betweenness centrality and eigenvalue centrality capture flow within the network more than a single link away. 
Unlike traversal funnels however, betweenness centrality and eigenvalue centrality reward nodes that simply happen to be in a cycle. 
In our sample network (see Fig.~\ref{fig:Centrality Measures}), node A is has betweenness centrality of 0.17 and eigenvalue centrality of 0.58 although node A is simply the recipient of paths directed by node C.
Eigenvector centrality even assigns the same centrality to nodes A, B, and C. In contrast, traversal funnels defines a path without a predetermined end node, following the progression of links to its culmination at the start of a cycle. Furthermore, traversal funnels provides an interpretable metric: a node's traversal funnels is the number of paths the node directs to the start of a cycle. 
Consequently, traversal funnels allow us to isolate the paths directed by node C without any spill over effect on other nodes in its cycle.

@@

By considering the FLN not only as collection of directly linked pairs of articles, but
as a flow using traversal funnels, with accumulated references, cycles, and path-connected groups, we explore how the many articles in Wikipedia are organized and related.
